\section{JavaScript evolution and role in web development}
The late 90s were characterised by brutal browser wars in the software industry\cite{wars}. These were mainly between Netscape's navigator and Microsoft's Internet explorer(IE).
\paragraph{}
Microsoft had developed their own JavaScript variants, VBScript and JScript. JScript was said to be a reverse engineering of JavaScript which was given a different name for legal reasons.
\paragraph{}
Having many languages for developing websites posed a lot of challenges for web developers. It meant that developers needed different codebases for different browsers. It lead to situations where browsers would have logos written "best viewed on IE" or "best viewed on Netscape navigator". A standard was needed so as to ease the process of developing websites.
\paragraph{}
In 1997 European Computer Manufacturers Association(ECMA) standardised JavaScript. The ECMA standards body could not get anyone to donate a trade mark, so they gave it the number ECMA-262. As a result JavaScript adopted the standards name ECMAScript. This led to major players like Microsoft adopting the use of JavaScript in their IE browsers.
\paragraph{}
The coming of IE4 extended JavaScript with XML first class object subtype literal syntax\cite{Eich:2005:JTY:1090189.1086382}. Later Asynchronous JavaScript and XML(AJAX) was later added to JavaScript which allowed browsers to interact with the server without reloading. With adoption from Microsoft, JavaScript eventually became the de facto language for web development.
\paragraph{}
Initially JavaScript was used to manipulate document object model(DOM) components so as to achieve pop-ups and animations. The coming of AJAX allowed developers to expand its usage to a wide range of applications.
\paragraph{}
Most Social media platforms started using it for single page applications. In single page applications, developers would leverage JavaScript features to achieve infinite scroll. Infinite scroll is used to simulate content delivery on demand for web applications as users scroll down \cite{ctx2425553500004041}. JavaScript also allowed to websites to dynamically renders advertisements after the page had loaded.



